A Comparison of Different GANs for Generating Handwritten Digits on MNIST

### 2020-04-11 proposal.tex
Went over experiment descriptions

@@

@@

\subsection{\label{sec:expTime}Time for Training}
% time for each generation? Sorta wishy washy on this one

@@

@@

@@

This project paves a useful survey and comparison of three popular GAN architectures. Based on the results we can conclude that....

>>>>

% used for the footnote
\usepackage{hyperref}

@@

The MNIST database of handwritten digits was used to test the GAN algorithms. The MNIST dataset comprises of seventy thousand handwritten digits already partitioned into a training and test set. The Training set contains sixty thousand images and ten thousand images are in the test set. This dataset was collected by using approximately 250 writers. Note: the writers in the training and test sets were disjoint from each other.

The MNIST dataset was selected because it is widely used in the field of computer vision and AI. Its popularity makes it an ideal dataset because we can compare our results with the work of other people. Since it is a large set that was used in prior papers, we also know that we could get a really good confidence score if we were solely creating a classifier. However, in this project we will be generating a discriminator and generator on the mnist set. Never-less, the dataset has proven by other researchers to be sufficient for use in neural networks. This  data is ideal to be used because all images are of fixed size of 20x20 and images have already been normalized.

Our data was downloaded from Yann LeCun's website \footnote{\url{http://yann.lecun.com/exdb/mnist/}}.

@@

In this experiment we aimed to test the quality of the images produced. In this test we had the GANS generate hand written digits. After scrambling which GAN produced which image, we asked a test participant to rank each image on a scale of 1-10 on how it looks. Ten would indicate that it looked like a human drew this digit and a one would indicate that the image looks bad. After all the data was collected we compared which GAN architecture had the best perceived quality from the participant.

\subsection{\label{sec:expTime}Training}
% time for each generation? Sorta wishy washy on this one

In this experement we cut off each GAN after a specif amount of Epochs. We compared the results of the three GAN architectures at 5, 15 and 30 Epochs.

@@

In this experiment we compare how the GAN algorithms run at different levels of training data from the MNIST set. We compare the GANS using the full training set, half the training set, and an eighth of the dataset.

@@

% TODO we might a dedicated results section

@@

This project is a useful survey and comparison of three popular GAN architectures. Based on the results we can conclude that....
